Documentation FFI Sonar Simulator

### 2013-05-22 FFI-Simulator/ffi-simulator.tex
la2pdf commit - 2013:05:22	11:55:24	(Wed22.May)

{\Large Design Suggestion} v2\\[0.2cm]
{\itshape for a}\\[0.2cm]
{\Large GPU Based Sonar Template Simulator}\\[2cm]
{\itshape by}\\[0.2cm]
\begin{minipage}{0.35\textwidth}\small\centering
Jo Inge \textsc{Buskenes}\\
\textnormal{\color{SeaGreen}joibu (at) ifi.uio.no}
\end{minipage}
\begin{minipage}{0.35\textwidth}\small\centering
Jon Petter \textsc{Åsen}\\
\textnormal{\color{SeaGreen}jpaasen (at) ifi.uio.no}
\end{minipage}\\[2cm]
{\itshape on the behalf of}\\[0.2cm]
\begin{minipage}[t]{0.49\textwidth}\centering
  \centering\includegraphics[height=3cm]{gfx/FFILogo.png}\\
  \textsc{The Norwegian Defence Research Establishment (FFI)}
\end{minipage}\\[0.5cm]
\begin{minipage}[t]{0.4\textwidth}\small\centering
Øivind \textsc{Midtgård}\\
\textnormal{\color{SeaGreen}oivind.midtgaard (at) ffi.no}
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}\small\centering
Herman \textsc{Midelfart}\\
\textnormal{\color{SeaGreen}herman.midelfart (at) ffi.no}
\end{minipage}\\[0.3cm]
\begin{minipage}{0.32\textwidth}\small\centering
Roy Edgar \textsc{Hansen}\\
\textnormal{\color{SeaGreen}roy-edgar.hansen (at) ffi.no}
\end{minipage}
\vfill
\small
\today
\end{center}

@@

@@

\begin{figure}[b]
\begin{narrow}{-2.5cm}{-2.5cm}
\graphicsAI[drawing,width=\linewidth]{gfx/simulator.svg}
\end{narrow}
\caption{Two possible implementation strategies.}\label{implementation}
\end{figure}

@@

In each of these cases the simulator takes a seafloor and target model as input, and generates a simulated sonar image.

@@

When we wish to set up a 3D scene, move objects and cameras around, and render it using a GPU, it is better to use e.g. OpenGL than CUDA/OpenGL. OpenGL was made for this specific task, is cross-platform, feature-rich and well-matured. By looking at the graphics quality and frame-rates displayed by modern OpenGL-based games it should also be fairly straight-forward to get the performance we need out of this library.

>>>>

{\Large Design Suggestion}\\[0.2cm]
{\itshape for a}\\[0.2cm]
{\Large GPU Based Sonar Template Simulator}\\[2cm]
{\itshape by}\\[0.2cm]
\begin{minipage}{0.35\textwidth}\small\centering
Jo Inge \textsc{Buskenes}\\
\textnormal{\color{SeaGreen}joibu (at) ifi.uio.no}
\end{minipage}
\begin{minipage}{0.35\textwidth}\small\centering
Jon Petter \textsc{Åsen}\\
\textnormal{\color{SeaGreen}jpaasen (at) ifi.uio.no}
\end{minipage}\\[2cm]
{\itshape on the behalf of}\\[0.2cm]
\begin{minipage}[t]{0.49\textwidth}\centering
  \centering\includegraphics[height=3cm]{gfx/FFILogo.png}\\
  \textsc{The Norwegian Defence Research Establishment (FFI)}
\end{minipage}\\[0.5cm]
\begin{minipage}[t]{0.4\textwidth}\small\centering
Øivind \textsc{Midtgård}\\
\textnormal{\color{SeaGreen}oivind.midtgaard (at) ffi.no}
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}\small\centering
Herman \textsc{Midelfart}\\
\textnormal{\color{SeaGreen}herman.midelfart (at) ffi.no}
\end{minipage}\\[0.3cm]
\begin{minipage}{0.32\textwidth}\small\centering
Roy Edgar \textsc{Hansen}\\
\textnormal{\color{SeaGreen}roy-edgar.hansen (at) ffi.no}
\end{minipage}
\vfill
\small
Revision 2, \today
\end{center}

@@

As detailed below, in this revision we have decided to opt for slightly more flexibile design to better be able to handle effects such as geometric layover.
% This is to better be able to simulate geometrical sonar imaging effects such as layover. We will describe both the original suggestions and the updated design here.

\subsection{The Initial Suggestion}

@@

\begin{figure}[b]
\begin{narrow}{-2.3cm}{-2.3cm}
\graphicsAI[drawing,width=\linewidth]{gfx/simulator.svg}
\end{narrow}
\caption{Two possible implementation strategies.}\label{implementation}
\end{figure}

@@

In each of these cases the simulator takes a seafloor and target model as input, and generates a simulated sonar image, as well as perform template correlation if desired. For the first step of setting up the 3D scene, move objects and cameras around, and render it using a GPU, we initially believed OpenGL to be the better choice. OpenGL was made for this specific task, is cross-platform, feature-rich, well-matured and tuned to peak performance to meet the heavy needs of the gaming industry.

But can we accurately simulate a sonar system using a framework designed to simulate optics?

\subsection{Geometrical Layover}

When we wish to , it is better to use e.g. OpenGL than CUDA/OpenGL.

@@
